\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-10 coqimpl.tex
more changes of wording: equality -> comp behavior

Upon \lsti{End}~\lsti{subst}, a module type named \lsti{STLC\_subst} is generated.
%
As discussed in \cref{sec:latebind}, \lsti{subst} can be further bound,
% \EDJ{If we don't allow further binding case handler(mentioned in your last reply), how do the user further bind the subst? I mean in the surface syntax}\YZreply{The position is that individual case handlers cannot be further bound, but the recursive function itself can be further bound by acquiring new case handlers.}
so its definition is not exposed to the fields that come after it.
Accordingly, the translation \lsti{STLC\_subst} merely declares the type of \lsti{subst}
and the equalities about its computational behaviors, leaving \lsti{subst} undefined
and the equalities unproven.
%
The equalities are stated in terms of the case handlers,
whose definitions \emph{are} available through the \lsti{self} parameter.
So Coq can simplify, for example, the type of \lsti{subst_tm_unit_eq} to
\lsti[basicstyle=\fontsize{8.5}{9},basewidth=.95ex]{\forall x t, self.subst self.tm_unit x t = self.tm_unit}.
These equalities about the computational bahaviors of \lsti{subst}
will be included and available for use in the translations of the
subsequent fields through their \lsti{self} parameters.

@@

In family \lsti{STLC},
field \lsti{env} and the case handlers for \lsti{subst}
are not further-bindable by derived families.
In contrast, \lsti{tm}, \lsti{subst}, and the related equalities
can be further bound.
The distinction is reflected in the translations.
The further-bindable fields are translated to module types that export only types of the fields.
The non-further-bindable fields are translated to modules that export definitional equalities
on the fields.
Opaque fields can be further bound, too (\cref{sec:override});
they are translated to modules that export opaque fields.

@@

\item
In \cref{fig:stlc-compiled},
an inductive type \lsti{tm} is generated, instantiating the axiomatized
\lsti{tm} type and its constructors.
%
The partial recursor \lsti{tm_prect_STLC} is defined
%to \lsti{\lambda}\,\lsti{P, tm_rect (\lambda}\,\lsti{t, option (P t))},
with the help of \lsti{tm_rect}, the recursor Coq generates for \lsti{tm}.
Proving the equalities on \lsti{tm_prect_STLC} is then trivial, by \lsti{reflexivity}.

\item
Similarly, \lsti{subst} is instantiated by applying the recursor \lsti{tm_rect}
to the (already included) case handlers. %(\lsti{subst\_tm_unit}, etc.).
Propositional equalities on \lsti{subst} are then trivial, by \lsti{reflexivity}.

>>>>

Upon \lsti{End}~\lsti{subst}, a module type named \lsti{STLC\_subst} is generated.
%
As discussed in \cref{sec:latebind}, \lsti{subst} can be further bound,
% \EDJ{If we don't allow further binding case handler(mentioned in your last reply), how do the user further bind the subst? I mean in the surface syntax}\YZreply{The position is that individual case handlers cannot be further bound, but the recursive function itself can be further bound by acquiring new case handlers.}
so its definition is not exposed to the fields that come after it.
Accordingly, the translation \lsti{STLC\_subst} merely declares the types of \lsti{subst}
and the equalities about its computational behaviors, leaving \lsti{subst} undefined
and the equalities unproven.
%
The equalities are stated in terms of the case handlers,
whose definitions \emph{are} available through the \lsti{self} parameter.
So Coq can simplify, for example, the type of \lsti{subst_tm_unit_eq} to
\lsti[basicstyle=\fontsize{8.5}{9},basewidth=.95ex]{\forall x t, self.subst self.tm_unit x t = self.tm_unit}.
These equalities about the computational bahaviors of \lsti{subst}
will be included and available for use in the translations of the
subsequent fields through their \lsti{self} parameters.

@@

In family \lsti{STLC},
field \lsti{env} and the case handlers for \lsti{subst}
are not further-bindable by derived families.
In contrast, \lsti{tm}, \lsti{subst}, and the related equalities
can be further bound.
The distinction is reflected in the translations.
The further-bindable fields are translated to module types that export only types of the fields.
The non-further-bindable fields are translated to modules that export definitional equalities
on the fields.
Opaque fields in \Lang can be further bound (\cref{sec:override});
they are translated to Coq modules that export opaque fields.

@@

\item
In \cref{fig:stlc-compiled},
an inductive type \lsti{tm} is generated, instantiating the axiomatized
\lsti{tm} type and its constructors.
%
The partial recursor \lsti{tm_prect_STLC} is defined
%to \lsti{\lambda}\,\lsti{P, tm_rect (\lambda}\,\lsti{t, option (P t))},
with the help of \lsti{tm_rect}, the recursor Coq generates for \lsti{tm}.
Computational behaviors of \lsti{tm_prect_STLC} are immediate, by \lsti{reflexivity}.

\item
Similarly, \lsti{subst} is instantiated by applying the recursor \lsti{tm_rect}
to the (already included) case handlers. %(\lsti{subst\_tm_unit}, etc.).
Computational behaviors of \lsti{subst} are then immediate, by \lsti{reflexivity}.
